My title

### 2024-03-31 paper/paper.qmd
update paper
redownload the raw data, updated the table of vairables in paper, and updated data_cleaning.R

| Variable | New Name  | Description                   | Example |
|----------|-----------|-------------------------------|---------|
| sex      | SEX       | Respondent's gender           | Female  |
| age      | AGE       | Respondent's age              | 25      |
| HEALTH   | health    | Respondents' health condition | Good    |
| PHYSHLTH | phys_days | Days of Respondents' physical health being not good   | 15      |
| MNTLHLTH | ment_days | Days of Respondents' mental health being not good     | 20      |
| DEPRESS  | depress   | Whether respondents have been told having depression  | Yes     |

@@

# Additional data details

>>>>

| Variable | New Name  | Description                   | Example |
|----------|-----------|-------------------------------|---------|
| SEX      | sex       | Respondent's gender           | Female  |
| AGE      | age       | Respondent's age              | 25      |
| HEALTH   | health    | Respondents' health condition | Good    |
| YEAR     | year      | Year of the Data Recorded     | 1977    |
| PHYSHLTH | phys_days | Days of Respondents' physical health being not good   | 15      |
| MNTLHLTH | ment_days | Days of Respondents' mental health being not good     | 20      |
| DEPRESS  | depress   | Whether respondents have been told having depression  | Yes     |

@@

## Additional data details
